---
title: "Estimate drugs synergy with synerdrug"
date: "`r Sys.Date()`"
output: 
    rmarkdown::html_vignette:
        toc: true
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
  
---

```{r, echo = FALSE}
require(knitr)
opts_chunk$set(echo = TRUE, fig.width = 5, fig.height = 4, prompt = TRUE, warning = FALSE)
```


```{r}
require(synerdrug)
data(exDrugSyn)
```

```{r}
exDrugSyn
drugNames(exDrugSyn)
doses(exDrugSyn)
```

## Visualise data

The data can be visualized by using `plot` on the `DrugSyn` object. Several visualization types are available: as heatmaps, as surface or parallel lines. 

```{r}
plot(exDrugSyn)
```

The data can be viewed as a surface by setting the `type` argument of `plot` to `"surface"`. Arguments from `persp` can be passed to plot to adjust the appearance (e.g. azimuth and co-latitude).

```{r}
plot(exDrugSyn, type = "surface")
plot(exDrugSyn, type = "surface", theta = -45, phi = 45)
```

```{r, fig.height = 3, fig.width = 6}
plot(exDrugSyn, type = "parallel", ref = "A")
plot(exDrugSyn, type = "parallel", ref = "B")

```


## Individual responses

The single agent responses are fitted by a Hill function (also known as log-logistic model or sigmoid curve) with 4 parameters:

$$E=E_0 + \frac{E_{max}-E_0}{1 + (\frac{EC_{50}}{d})^n}$$

where:

* $E$ is the observed effect
* $d$ is the dose
* $E_0$ is the minimum effect
* $E_{max}$ is the maximum effect
* $EC_{50}$ is the effective dose 50
* $n$ is the sigmoidicity parameter.

```{r, fig.height = 3, fig.width = 6}
plot(exDrugSyn, type = "ind", drug = "A")
plot(exDrugSyn, type = "ind", drug = "B")
```

The parameters of the hill functions can be accessed with `respInd`.
```{r}
respInd(exDrugSyn)
```



## Synergy estimates

Several synergy estimate idexes are computed by `synerdrug`. 

### Effect-based synergy evaluation
 $HSA_{ab}=max(E_{a0}, E_{0b})/E_{ab}$;
 
  $Bliss_{ab}=(E_{a0}+E_{0b}-E_{a0}E_{0b})/E_{ab}$
  
```{r}

plot(exDrugSyn, type = "heatmap", what = "Bliss")
plot(exDrugSyn, type = "surface", what = "LoeweExcess")

```

### Dose-effect based synergy evaluation

$a/A+b/B=1$

$CI_{ab}=a/A+b/B$  

## Isobologram
```{r}
isobologram(exDrugSyn, effect = 0.5)
isobologram(exDrugSyn, effect = 0.5, mode = "SP")
```





